Rust Bug Fix Patterns

### 2022-09-20 methodology.tex
token type to dimension item, maybe there exists a better word choice, one can always use cmd+R

% I need to reread this key paragraph. - PL
A simple heuristic is that, the closer we get to the leaves in the ASTDiff, the more important dimension items get. Another observation is that the elements closer to the root tend to be repeated in all the paths within one ASTDiff (e.g. ItemFn, Local, ExprCall in Figure~\ref{fig:extraction}). Exploiting the latter observation, to obtain a basic knowledge about the number of repetitions of dimension items, we mined the last 20 bug related commits of the last 20 most starred rust projects on GitHub, and ran them through of pipeline. We recorded the number of occurrences of each token type in total. Then we gave the value of the inverse of the number of occurrences to each token. The intuition is that the higher the number of occurrences of a token type, the closer it is usually seen to the root. Hence, it probably does not provide us with the most accurate description of the change. In addition to that, as we wanted to make sure that our tool captures the patterns related to borrow checker, we manually raised the weights of the dimension items related to borrow checker. That is why we characterize our weighting scheme as semi-automatically designed.

>>>>

% I need to reread this key paragraph. - PL
A simple heuristic is that, the closer we get to the leaves in the ASTDiff, the more important dimension items get. Another observation is that the elements closer to the root tend to be repeated in all the paths within one ASTDiff (e.g. ItemFn, Local, ExprCall in Figure~\ref{fig:extraction}). Exploiting the latter observation, to obtain a basic knowledge about the number of repetitions of dimension items, we mined the last 20 bug related commits of the last 20 most starred rust projects on GitHub, and ran them through of pipeline. We recorded the number of occurrences of each dimension item in total. Then we gave the value of the inverse of the number of occurrences to each token. The intuition is that the higher the number of occurrences of a dimension item, the closer it is usually seen to the root. Hence, it probably does not provide us with the most accurate description of the change. In addition to that, as we wanted to make sure that our tool captures the patterns related to borrow checker, we manually raised the weights of the dimension items related to borrow checker. That is why we characterize our weighting scheme as semi-automatically designed.
